\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{libertine}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Rakesh Kumar} \\ \vspace{1pt}
    \small +91-8209211601 $|$ \href{mailto:rakesh.kumar.132457@gmail.com}{\underline{rakesh.kumar.132457@gmail.com}} $|$
    \href{https://linkedin.com/in/rakeshkumar1324}{\underline{linkedin.com/in/rakeshkumar1324}} $|$
    \href{https://github.com/RakeshKumar132457}{\underline{github.com/RakeshKumar132457}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer}{Dec 2022 -- Present}
{CarDekho}{Gurgaon}
\resumeItemListStart
\resumeItem{Contributed to a new NestJS and GraphQL project; spearheaded 3 key features end-to-end, including frontend UI, data modeling, and backend resolvers, adhering to PRD specifications and improving data retrieval efficiency by 25\% for 200+ daily users.}
\resumeItem{Architected a flexible role-based access control system; designed database schema for roles and permissions, developed frontend module for role management, and established backend middleware for API validation, reducing unauthorized access attempts by 75\%.}
\resumeItem{Devised a comprehensive target-setting and performance tracking system, integrating CSV uploads, real-time achievement visualization, and mobile notifications, resulting in a 30\% increase in user goal attainment.}
\resumeItem{Crafted a PDF microservice with customizable templates and data injection; reduced generation time from 15-20 seconds to under 5 seconds, supporting 13,700+ monthly reports, invoices, and forms across multiple services.}
\resumeItem{Developed a role-based form system for dealership visits, featuring customizable questions and instant dealer acknowledgment, reducing form completion time from hours to 4-5 minutes and eliminating data loss.}
\resumeItemListEnd

\resumeSubheading
{Engineer}{Dec 2021 -- Dec 2022}
{Mindtree}{Bengaluru}
\resumeItemListStart
\resumeItem{Constructed comprehensive test automation framework; incorporated page object model, data-driven testing, and parallel execution, resulting in 61\% task automation and 48\% faster testing cycles.}
\resumeItem{Managed development and maintenance of client-specific RESTful APIs; enhanced system reliability and error handling, improving overall functionality by 59\% and ensuring adherence to diverse client requirements.}
\resumeItem{Executed comprehensive security measures across API endpoints and frontend; leveraged open-source vulnerability scanners and internal tools to conduct audits, mitigating 97\% of common vulnerabilities and enhancing overall application security.}
\resumeItem{Co-led a team of 20 interns with one other mentor; designed and conducted full-stack training program covering Node.js, MySQL, and React, resulting in 80\% conversion rate to full-time positions, significantly above company average.}
\resumeItemListEnd

\resumeSubheading
{Trainee Engineer}{Sep 2020 -- Mar 2021}
{KloudGin}{Hyderabad}
\resumeItemListStart
\resumeItem{Integrated ArcGIS feature in Angular; refined map rendering and devised custom controls, achieving 39\% faster visualization and 28\% quicker queries for 10,000+ daily active users.}
\resumeItem{Created a Java-based tool interfacing with AWS CLI for QuickSight; automated report generation and dashboard creation, streamlining BI workflow and reducing end-to-end process time by 46\%.}
\resumeItem{Optimized advanced features in agGrid; enhanced rendering for 1M+ records, resulting in 27\% faster data loading times and enabling custom filtering and export options.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------KEY PROJECTS-----------
\section{Key Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Journey} $|$ \emph{Node.js, Express, React, MySQL, MongoDB}}{}
\resumeItemListStart
\resumeItem{Architected a sophisticated multi-tier evaluation system for 40,000+ financial agents, integrating configurable performance metrics and automated grading algorithms.}
\resumeItem{Established a 5-tier hierarchical approval workflow, reducing evaluation time by 80\%, significantly improving process efficiency.}
\resumeItem{Streamlined final approval process, reducing processing time by 95\% and eliminating manual data transfer errors.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Notification Module} $|$ \emph{Node.js, React, Google Pub/Sub, Cloud Scheduler, MySQL}}{}
\resumeItemListStart
\resumeItem{Engineered a flexible notification system with customizable types, frequency, and duration, improving user engagement by 37\%.}
\resumeItem{Deployed robust user targeting via CSV uploads and business line/role filters, enabling precise communication to 50+ user segments.}
\resumeItem{Leveraged Google Pub/Sub and Cloud Scheduler for efficient notification processing, achieving 97\% delivery within 3 minutes during peak loads without system degradation.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Web Security Assessment Platform} $|$ \emph{Angular, TypeScript, Node.js, Express}}{}
\resumeItemListStart
\resumeItem{Conceptualized and built an interactive platform showcasing OWASP Top 10 vulnerabilities with hands-on exercises.}
\resumeItem{Synthesized real-world scenarios into practical learning modules, garnering a 4.7/5 average rating from 150+ participants.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Chandigarh University}{Punjab, India}
{Bachelor of Engineering in Computer Science}{Aug 2017 -- May 2021}
\resumeItemListStart
\resumeItem{Developed an AI-powered assistant using Python, integrating Wolfram Alpha and Wikipedia APIs; implemented natural language processing for query interpretation, achieving 87\% accuracy in providing relevant information across diverse topics.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
          \textbf{Languages}: JavaScript (ES6+), TypeScript, Python, Java, C/C++, SQL \\
          \textbf{Frontend}: React, Angular, HTML5, CSS3, SCSS, Tailwind, Bootstrap \\
          \textbf{Backend}: Node.js, Express.js, NestJS, Django \\
          \textbf{Databases}: MongoDB, MySQL, PostgreSQL, Redis \\
          \textbf{Cloud \& DevOps}: AWS (EC2, S3, QuickSight), GCP, Docker, Jenkins \\
          \textbf{Testing}: Jest, Selenium, JUnit \\
          \textbf{Tools \& Methodologies}: Git, JIRA, RESTful APIs, GraphQL, Microservices, Agile/Scrum, TDD
          }}
\end{itemize}

\end{document}